---
title: "Worked Example 2 - Main Population Calculations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Worked Example 2 - Main Population Calculations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is an example of how to load a dataset and carry out simulations of the progression of malaria in the main (non-cohort) population.

First load the package (install it first if necessary as shown in the [Installation article](https://keithjf82.github.io/vectorpower/articles/B_installation.html):

```{r}
library(vectorpower)
```

Next create the list of input file locations to supply to the mainpop() function.  Here the files are located online, so the list is created manually:

```{r}
input_files <- list(
  param_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/model_parameters_const.txt"),
  age_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/age_data_145.txt"),
  het_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/het_data_9.txt"),
  start_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/start_data_example.txt"),
  annual_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/annual_data_example.txt")
                    )
```

If using a dataset folder created using dataset_create(), this can be done automatically by using the load_dataset() function. Here the example folder in the inst/extdata subfolder, created in the first worked example, is used:

```{r, eval=FALSE}
dataset_folder=system.file("extdata/Demo Folder 1/",package="vectorpower")
input_files <- load_dataset(dataset_folder)

```

The parameters defining the trial setup are then supplied to be used by mainpop():

```{r}
# Length of time to run main population model from starting date before intervention begins
start_interval = 0.0  
# Time points after the end of the starting interval at which benchmark data should be output
time_values = c(0.0,28.0,56.0,84.0,112.0,140.0) 
# List of sets of values to load from starting data
n_mv_set = c(1:5) 
# Intervention parameter given variable value (0= None, 1=ATSB kill rate, 2=bednet coverage, 3=IRS coverage)
int_v_varied = 1 
# List of intervention parameter values
int_values = c(0.0,0.1) 
```

The parameters and list of input files are then passed to the mainpop() function:

```{r}
mainpop_data <- mainpop(input_files = input_files, n_mv_set = n_mv_set, int_v_varied = int_v_varied, 
                        int_values=int_values, start_interval = start_interval, time_values=time_values)
```

The resulting data can be used in cohort calculations or processed on its own. It can be saved to a file so that it can be used again if R is closed. In this example, it is saved to a file inside the inst/extdata sub-folder (overwriting an identical existing file).

```{r}
setwd(system.file("extdata",package="vectorpower"))
saveRDS(mainpop_data,file="mainpop_data1.Rds")
```

The plot_mainpop_data() function can be used to plot selected results:

```{r}
par(mfrow=c(1,2))
plot1 <- plot_mainpop_data(input_list=mainpop_data,set_n_int=1,benchmark="slide_prev",age_start=0.0,age_end = 65.0)
plot2 <- plot_mainpop_data(input_list=mainpop_data,set_n_int=2,benchmark="slide_prev",age_start=0.0,age_end = 65.0)
par(mfrow=c(1,1))
```

