---
title: "Worked Example 2 - Main Population Calculations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Worked Example 2 - Main Population Calculations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_chunk$set(root.dir = system.file("extdata",package="vectorpower"))
```

This is an example of how to load a dataset and carry out simulations of the progression of malaria in the main (non-cohort) population.

First load the package (install it first if necessary as shown in the [Installation article](https://keithjf82.github.io/vectorpower/articles/B_installation.html):

```{r}
library(vectorpower)
```

Next create the list of input file locations to supply to the mainpop() function.  Here the files are located online, so the list is created manually:

```{r}
input_files <- list(
  param_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/DemoFolder1/model_parameters.txt"),
  age_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/DemoFolder1/age_data.txt"),
  het_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/DemoFolder1/het_data.txt"),
  start_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/DemoFolder1/start_data.txt"),
  annual_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/DemoFolder1/annual_data.txt")
                    )
```

If using a dataset folder created using dataset_create(), this can be done automatically by using the load_dataset() function. Here the example folder in the inst/extdata subfolder, created in the first worked example, is used:

```{r, eval=FALSE}
dataset_folder=system.file("extdata/DemoFolder1/",package="vectorpower")
input_files <- load_dataset(dataset_folder)
```

The parameters defining the trial setup are then supplied to be used by mainpop():

```{r}
# Length of time to run main population model from starting date before intervention begins
start_interval = 0.0  
# Time points after the end of the starting interval at which benchmark data should be output
time_values = c(0.0,28.0,56.0,84.0,112.0,140.0) 
# List of sets of values to load from starting data
n_mv_set = c(1:5) 
# Intervention parameter given variable value (0= None, 1=ATSB kill rate, 2=bednet coverage, 3=IRS coverage)
int_v_varied = 1 
# List of intervention parameter values
int_values = c(0.0,0.1) 
```

The parameters and list of input files are then passed to the mainpop() function, which runs the deterministic continuum malaria model, the code for which is found in mainpop.cpp in the src/ folder.

```{r}
mainpop_data <- mainpop(input_files = input_files, n_mv_set = n_mv_set, int_v_varied = int_v_varied, 
                        int_values=int_values, start_interval = start_interval, time_values=time_values)
```

The resulting data can be used in cohort calculations or processed on its own. It can be saved to a file so that it can be used again if R is closed.

```{r, eval=FALSE}
saveRDS(mainpop_data,file="mainpop_data.Rds")
```

The get_mainpop_data() function can be used to plot selected results:

```{r}
par(mfrow=c(1,2))
plot1 <- get_mainpop_data(input_list=mainpop_data,set_n_int=1,benchmark="slide_prev",age_start=0.0,age_end = 65.0,plot_flag=TRUE)
plot2 <- get_mainpop_data(input_list=mainpop_data,set_n_int=2,benchmark="slide_prev",age_start=0.0,age_end = 65.0,plot_flag=TRUE)
par(mfrow=c(1,1))
```

For the creation of cohort data from main population data, see [Worked Example 3](https://keithjf82.github.io/vectorpower/articles/E_worked_example03.html).
