---
title: "worked_example2_mainpop_only"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{worked_example2_mainpop_only}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Worked example 2 - Running main population calculations

This is an example of how to load a dataset and carry out simulations of the progression of malaria in the main (non-cohort) population.

First load the package (install it first if necessary as shown in the Installation article)

```{r, eval = FALSE}
library(vectorpower)
```

Next create the list of input file locations to supply to the mainpop() function. If using a dataset folder created using dataset_create(), this can be done automatically by using load_dataset(dataset_folder=[folder location]). Here the files are located online, so the list is created manually:

```{r, eval = FALSE}
input_files <- list(
  param_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/model_parameters_const.txt"),
  age_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/age_data_145.txt"),
  het_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/het_data_9.txt"),
  start_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/start_data_example.txt"),
  annual_file=url("https://raw.githubusercontent.com/KeithJF82/vectorpower/master/inst/extdata/param_examples/annual_data_example.txt")
                    )
```

The parameters defining the trial setup are then supplied to be used by mainpop().

```{r, eval = FALSE}
start_interval = 0.0  # Length of time to run main population model from starting date before intervention begins
time_values = c(0.0,28.0,56.0,84.0,112.0,140.0) # Time points after the end of the starting interval at which benchmark data should be output
n_mv_set = c(1:5) # List of sets of values to load from starting data
int_v_varied = 1 # Intervention parameter given variable value (0= None, 1=ATSB kill rate, 2=bednet coverage, 3=IRS coverage)
int_values = c(0.0,0.1) # List of intervention parameter values
```

The parameters and list of input files are then passed to the mainpop() function:


```{r, eval = FALSE}
mainpop_data1 <- mainpop(input_files = input_files, n_mv_set = n_mv_set, int_v_varied = int_v_varied, int_values=int_values,
                         start_interval = start_interval, time_values=time_values)
```


